---
title: "SC19: Quiz 01"
date: "October 16, 2019. 1:30 PM -- 2:30 PM"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(GGally)
```

# Problem 1 [20 pts]

### From the wine data given, reproduce the following plots as exactly as possible. Do not change size, alpha, and coordinate range from the default setting.

```{r, echo = TRUE, message= FALSE}
wine <- read_csv("./quiz-1.csv")
head(wine)
```


**a) [8 pts]**

```{r}
ggplot(wine, aes(volatile_acidity, residual_sugar, color=quality)) +
  geom_point() +
  facet_wrap(.~type, nrow=2) +
  scale_x_log10() +
  scale_y_log10()

```


**b) [12 pts]**

```{r}
ggplot(wine, aes(x=type)) +
  geom_bar(aes(fill=quality), position="dodge") +
  coord_flip() +
  labs(
    title = "Summary on wine qualities",
    subtitle = "119 red wines, 224 white wines",
    x = NULL,
    y = NULL
  ) +
  theme(legend.position = "top")

```


# Problem 2 [20 pts]

### We give you the following `lam_wf` data; every subproblem in problem 2 uses this dataset. This data set is the simplified version of the datasets that consists of the engineering variables from a LAM 9600 Metal Etcher over the course of etching 129 wafers. For more information about the original data set, please see:

```
B.M. Wise, N.B. Gallagher, S.W. Butler, D.D. White, Jr. and G.G. Barna, \"A Comparison of Principal Components Analysis, Multi-way Principal Components Analysis, Tri-linear Decomposition and Parallel Factor Analysis for Fault Detection in a Semiconductor Etch Process\", J. Chemometrics, in press, 1999
```

```{r, echo = TRUE, message= FALSE}
lam_wf <- read.csv('./lam_data.csv')
lam_wf %>% head
```


**a) [10 pts]**

```{r}
lam_wf %>% 
  group_by(batch_id) %>% 
  arrange(batch_id, Time) %>% 
  mutate(
    nearest_time = lag(Time),
    time_diff = abs(Time - nearest_time)
  ) %>% 
  summarize(
    mean_time_diff = mean(time_diff, na.rm = TRUE)
  ) %>% 
  arrange(desc(mean_time_diff))
  
```

> Batch l2903.txm	has maximum mean time difference with 1.06

**b) [10 pts]**

```{r}
lam_wf %>% 
  group_by(batch_id, Step_Number) %>% 
  summarize(mean_pressure = mean(Pressure)) %>% 
  group_by(batch_id) %>% 
  filter(min_rank(desc(mean_pressure)) == 1)
```

> 4 is the most common step number that showed maximum mean pressure.

## Problem 3 [20 pts]

### To consider factors affecting students' score, one collects `students` data from a class.

```{r, echo = TRUE, message= FALSE}
students_columns <- c(
  "student_number", # index of student
  "absence",        # number of absence
  "age",            # age in years
  "alcohol",        # average bottles student drinks in a week
  "major",          # major
  "studytime",      # average hours student study in a week
  "retake",         # does student retake this course?
  "score"           # score
)

students <- read_csv("./students.csv", col_types = cols(),
  col_names = students_columns) %>%
  mutate(
    absence = as.factor(absence),
    alcohol = as.factor(alcohol)
  )

students

```

**a) [4 pts] **

```{r}
summary(students)

students %>% 
  arrange(desc(age))

students <- students %>% filter(student_number != 34)
```

> There is a student with age 200, which is hardly possible. The student number is 34, so I deleted the row.

**b) [4 pts]**

```{r}
(tbl <- as.tbl(students[c("studytime", "retake", "score")]))

ggpairs(
  tbl,
  upper = list(
    combo = "box_no_facet"
  ),
  diag = list(
    continuous = "barDiag"
  ),
  lower = list(
    continuous = "smooth"
  )
)

```

> "yes" with retake have higher mean studytime than with "no". And "yes" with retake also have higher mean score than with "no". Studytime have a positive corrleation with score, but with some variance.

**c) [4 pts]**

```{r}
ggplot(students, aes(studytime, score)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~major)
```

> Still show positive correlation, except for the those who majored in "C" or "D".

**d) [4 pts]**

```{r}
ggplot(students, aes(alcohol, score)) +
  geom_boxplot()
```

> More alcohol is related with less score.

**e) [4 pts]**

```{r}
ggplot(students, aes(absence, score)) +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center"
  )
```

> More absence is related with less score.
